\input{shared_tex/geology.tex}
Slightly more than three quarters of the bedrock in the Town is part of the
Austin Glen Formation and composed of primarily graywacke and shale, which are
sedimentary types of carbonate rock. Given that there are still active shale
mines in Blooming Grove this does not come as a surprise. The first name in the
legend, in this case “Middle Ordovician” denotes what time period the geology
was formed. The formation is potentially calcareous, meaning it is mostly or
partly made up of calcium carbonate. The other large formations, at twelve and
seven percent respectively are Undifferentiated Hamilton Group and
Undifferentiated Lower Devonian and Silurian rocks. The former is mostly
comprised of shale and siltstone and the latter is composed of limestone and
dolostone. Siltstone is also another sedimentary rock and contains more quartz
than either mudstones or shales. The rock is formed by silt grade sediment in
either marine or freshwater environments being compacted. Limestone is rock
that is made up of mostly calcium carbonate. At just under five percent,
Garnet-biotite-quartz-feldspar gneiss is composed of gneiss and quartzite and
is the only other rock type that covers more than one percent of the town’s
area.

\subsection{soils}

\begin{table}[h!]
    %\centering
    \begin{tabular}{l l c c }
    Name & Acres & Percentage \\
    \hline
    MdC & 5665 & 18.50\%\\
    ErB & 1846 & 6.03\%\\
    RSD & 1804 & 5.89\%  \\
    RSB & 1242 & 4.05\%\\
    Ab & 1009 & 3.29\%\\
    SXC & 914 & 2.98\%\\
    ANC & 870 & 2.84\%\\
    ANF & 840 & 2.74\% \\
    total & 20243 & 66\% &\\
    \end{tabular}
    \caption{Blooming Grove Soil Classes}
    \label{tab:BG_soil}
\end{table}